data_collation

### 2024-05-23 scripts/data_collation.Rmd
started script for figures

# Melt only columns AGH:WHEL into long format
Kelp_COVER_long <- Kelp_COVER %>%
  pivot_longer(cols = AGH:CLT, names_to = "SP_CODE", values_to = "value")

@@

# remove columns with observer and unneeded data
fish_data <- fish_data[ -c(10:14) ]

@@

# remove columns with VIS
fish_data <- fish_data[ -c(14) ]

@@

# output updated dataframe
write.csv(fish_data, "output/cleaned_data/fish.data.clean.csv", row.names = FALSE)

>>>>

# Melt only columns AGH:WHEL into long format
Kelp_COVER_long <- Kelp_COVER %>%
  pivot_longer(cols = AGH:CLT, names_to = "SP_CODE", values_to = "COVER")

@@

# remove columns with observer and unneeded data
fish_data <- fish_data[ -c(10:13) ]

@@

@@

#combine with fish aggregated data
fish_data_agg <- rbind.fill(fish_data, fish_Aggregated)

# remove columns with X fromm numerical order of columns
fish_data_agg <- fish_data_agg[ -c(16) ]

# Rename ft. wetherill to fort wetherill
fish_data_agg$SITE[fish_data_agg$SITE == "Kings Beach"] <- "King's Beach"

# Rename fort weatherill
fish_data_agg$SITE[fish_data_agg$SITE == "Fort Weatherill"] <- "Fort Wetherill"

# Rename transcets to not have FW or KB before them
fish_data_agg$TRANSECT <- gsub("FW\\s*", "", fish_data_agg$TRANSECT)
fish_data_agg$TRANSECT <- gsub("KB\\s*", "", fish_data_agg$TRANSECT)

# output updated dataframe
write.csv(fish_data_agg, "output/cleaned_data/fish.data.clean.csv", row.names = FALSE)
